Programs Performance Analysis Toolkit

### 2013-10-08 keynote/Keynote.tex
Add more slides on implementation

@@

\section{Implementation}

@@

>>>>

\graphicspath{{../doc/pictures/}}

@@

\section{Implementation (general info)}

@@

\begin{frame}
\frametitle{Technology stack}

	\begin{itemize}
		\item Database server
		\begin{itemize}
			\item Distributed client-server document-oriented storage \textit{CouchDB}
			\item Cloud platform \textit{Cloudant}
		\end{itemize}
		\item Client
		\begin{itemize}
			\item \textit{Python}
			\item Statistical framework \textit{Orange}
			\item \textit{GNU/Linux} on \textit{x86} platform
		\end{itemize}
	\end{itemize}

\section{Implementation (client)}

\begin{frame}
\frametitle{Database interaction module}

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Provides high-level API for storage of \textit{Python} objects to database documents
				\item Uses local \textit{CouchDB} server as a fall-back if the remote isn't available
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{database-interaction}
			\end{figure}
		\end{column}
	\end{columns}

\begin{frame}
\frametitle{Program building module}

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Manages paths to source files of experimental programs
				\begin{itemize}
					\item Sources are in hierarchical structure of directories
					\item Module enables that only specifying the name of program to build is enough for sources to be found
				\end{itemize}
				\item Manages build tools and their settings
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{source-tree}
			\end{figure}
		\end{column}
	\end{columns}

\begin{frame}
\frametitle{Experimentation module}

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Calibrates the program execution time measurement before every series of runs
				\begin{itemize}
					\item Subtracts the execution time of ''simplest'' program to avoid systematical error
					\item Runs the program being studied until relative  dispersion of time measurement becomes pretty low ($d_{rel} < 5\%$)
				\end{itemize}
				\item Passes the experiment data to the database interaction module
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{console}
			\end{figure}
		\end{column}
	\end{columns}

\begin{frame}
\frametitle{Information retrieval module}

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Collects the information on used platform and experiment being carried out
				\item CPU
				\begin{itemize}
					\item Frequency
					\item Cache size
					\item Instruction set extensions
					\item etc.
				\end{itemize}

			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Compiler
				\item Experiment
				\begin{itemize}
					\item Studied program
					\item Size of input data
				\end{itemize}
			\end{itemize}
		\end{column}
	\end{columns}
